---
title: "Homework 1"
author: "Jerry Chao UNI jyc2171"
date: 2019-09-17
output: github_document
---

### This is my solution to Problem 1.

```{r setup, include = FALSE} 
library(tidyverse)
```

#### Data frame comprised of the specified elements is as below:

```{r US_states_df}
US_states_df = 
  tibble(
     Sample = rnorm(10),
     Sample_gt_0 = Sample > 0,
     States = c("New York", "California", "Rhode Island", "Maine", "Missouri", "Connecticut", 
                "New Jersey", "Pennsylvania", "Washington", "South Dakota"),
     Time_zone = factor(c("Eastern", "Pacific", "Eastern", "Eastern", "Central", "Eastern",                                 "Eastern", "Eastern", "Pacific", "Central")),
)
US_states_df
```

#### Next, I try to take the mean of each variable.

```{r mean}
mean(pull(US_states_df, Sample))
mean(pull(US_states_df, Sample_gt_0))
mean(pull(US_states_df, States))
mean(pull(US_states_df, Time_zone))
```

#### I can take the mean of numbers and logical but not character or factor.

```{r numeric_conversion, eval = FALSE}
as.numeric(pull(US_states_df, Sample))
as.numeric(pull(US_states_df, Sample_gt_0))
as.numeric(pull(US_states_df, States))
as.numeric(pull(US_states_df, Time_zone))
```

#### Number, logical, and factor variables can be converted to numbers.  Character variables cannot be converted to numbers.

#### Next, I convert variables from one type to another as specified:

```{r convert, eval = FALSE}
as.numeric(pull(US_states_df, Sample_gt_0)) * pull(US_states_df, Sample)
as.factor(pull(US_states_df, Sample_gt_0)) * pull(US_states_df, Sample)
as.numeric(as.factor(pull(US_states_df, Sample_gt_0))) * pull(US_states_df, Sample)
```

#### The logical converted to numeric ranges from 0 to 1.  The product is numbers.
#### The logical converted to factor yields "TRUE" or "FALSE".  The product is not meaningful.
#### The logical converted to factor, then converted to numeric ranges from 1 to 2 (instead of 0 to 1 for some reason).  The product is numbers.

### This is my solution to Problem 2.

#### Loading the downloaded "Penguins" dataset:

```{r load_penguin}
data("penguins", package = "palmerpenguins")
```

#### This dataset appears to be a data frame consisting of `r ncol(penguins)` columns and `r nrow(penguins)` rows.  There are three factor variables indicating the species, island (of origin?), and biologic sex of the penguins.  
#### There are three types of species: Adelie, Gentoo, and Chinstrap.
#### There are three types of islands: Biscoe, Dream, and Torgeren
#### The length (in millimeters), mass (in grams), and year are integer variables.
#### The bill length (millimeters) and bill depth (millimeters) are also numbers and appear to be to the tenths decimal place.  There are missing data as indicated by "NA" in various fields.  The mean flipper length is `r mean(pull(penguins, flipper_length_mm))`.

Next, I make a scatterplot of flipper length and bill length with color points defined by species.  The first step is creating the data frame.

```{r df_create}
scatterplot_df = tibble(
  x = pull(penguins, bill_length_mm),
  y = pull(penguins, flipper_length_mm),
  z = pull(penguins, species)
)
```

Next, I will generate the scatterplot:

```{r yx_scatter}
ggplot(scatterplot_df, aes(x = x, y = y, color = z)) + geom_point()
```
